\documentclass[12pt]{article}

\addtolength{\textwidth}{1.4in}
\addtolength{\oddsidemargin}{-.7in} %left margin
\addtolength{\evensidemargin}{-.7in}
\setlength{\textheight}{8.5in}
\setlength{\topmargin}{0.0in}
\setlength{\headsep}{0.0in}
\setlength{\headheight}{0.0in}
\setlength{\footskip}{.5in}
\renewcommand{\baselinestretch}{1.0}
\setlength{\parindent}{0pt}
\linespread{1.1}

\usepackage{amssymb, amsmath, amsthm, bm}
\usepackage{graphicx,csquotes,verbatim}
\usepackage[backend=biber,block=space,style=authoryear]{biblatex}
\setlength{\bibitemsep}{\baselineskip}
\usepackage[american]{babel}
%dell laptop
\addbibresource{C:/Users/Kristy/Dropbox/Research/xBibs/tradeagreements.bib}
%\addbibresource{C:/Users/Kristy/Documents/Dropbox/Research/xBibs/tradeagreements.bib}
\renewcommand{\newunitpunct}{,}
\renewbibmacro{in:}{}


\DeclareMathOperator*{\argmax}{arg\,max}
\usepackage{xcolor}
\hbadness=10000

\newcommand{\ve}{\varepsilon}
\newcommand{\ov}{\overline}
\newcommand{\un}{\underline}
\newcommand{\ta}{\theta}
\newcommand{\al}{\alpha}
\newcommand{\Ta}{\Theta}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\Bt}{B(\bm{\tau^a})}
\newcommand{\bta}{\bm{\tau^a}}
\newcommand{\btn}{\bm{\tau^n}}
\newcommand{\ga}{\gamma}
\newcommand{\Ga}{\Gamma}
\newcommand{\de}{\delta}


\title{Problems with Dropbox}
\author{Kristy \& Frank}

\begin{document}
\maketitle


\vskip.2in
\begin{enumerate}
	\item Bad at dealing with simultaneous changes: ``I never make changes, edit or work with files in dropbox. That’s a very bad idea. Dropbox is very poor at dealing with simultaneous changes to a document.'' (\url{http://www.whooshtranscription.com/dropbox-review/})
		\begin{itemize}
			\item Conflicted copies. These happen any time two people update a file at the same time. Or one person updates a file on a second device when the first has not synced. i.e. ``at the same time'' only means that a sync has not occurred. (\url{http://nerdenterprises.com/blog/2011/05/how-to-avoid-conflicting-copies-in-drop-box/})
			\begin{itemize}
				\item Procedure for creating conflicted copy with oneself
					\begin{enumerate}
						\item Create file and wait for it to sync to Dropbox and then down to second device
						\item Disconnect second device from internet
						\item Make a change to each file (even the exact same change)
						\item Reconnect second device to the internet. Wait for sync to occur
						\item Voil\`{a}
					\end{enumerate}
				\item Much easier to create conflicted copy with a collaborator...
			\end{itemize}
		\end{itemize}
	\item Automatic sync does not always work. Not clear how to replicate this. (\url{http://www.whooshtranscription.com/dropbox-review/}). Some possibilities:
		\begin{itemize}
		  \item Dropbox mea culpa about OS incompatibilities (\url{https://www.dropbox.com/en/help/145})
			\item Confusion about two different types of ``sharing;'' one only sends the files once; the other sends all future updates as well \\ (\url{http://simonhackett.com/2013/04/05/dropbox-sharing-doesnt-work-and-the-fi/})
		\end{itemize}
	\item 30-day retrieval: ``For a free account any file deleted in the in the last 30 days can be undeleted.'' (\url{http://www.whooshtranscription.com/dropbox-review/})
		\begin{itemize}
			\item If you have Dropbox Pro, you can purchase Extended Version History for $\$$39/yr to get 365-day retrieval
			\item Packrat was the same price with unlimited version history, but has been phased out
		\end{itemize}
	\item Files are deleted if anyone sharing them deletes them or moves them out of dropbox and disconnects the new location \\
	(\url{http://www.businessinsider.com/weird-feature-in-dropbox-deletes-files-2014-4})	
	\item Out of control directories with multiple date-stamped versions, futile attempts to use text files to keep records of what you've
done.
\end{enumerate}



\end{document}